Compositional equivalences based on Open pNets

### 2021-10-08 2016-Weak-FH-Bisim/WeakBisim.tex
minor

\begin{definition}[Semantics of pNets as a weak open automaton]
Let $A$ be the open automaton expressing the semantics of an open pNet $\pNet$; let $\mylangle J,\mathcal{S},s_0, V, \WT\myrangle$ be the weak open automaton derived from $A$; this weak open automaton defines the weak semantics of the pNet $\pNet$. Then, we denote $\pNet \models \WOT$ whenever $\WOT\in\WT$.
\end{definition}

@@

%where both a component and  its environment (other components) can be designed, by automata we find the theory of interface automata \cite {deAlfaro:2001} and conditional transition systems \cite{Beohar:2020}. Our formalism open automata is different from

>>>>

\begin{definition}[Semantics of pNets as a weak open automaton]
Let $A$ be the open automaton expressing the semantics of an open pNet $\pNet$; let $\mylangle J,\mathcal{S},s_0, V, \WT\myrangle$ be the weak open automaton derived from $A$; we call this weak open automaton the weak semantics of the pNet $\pNet$. Then, we denote $\pNet \models \WOT$ whenever $\WOT\in\WT$.
\end{definition}

@@

%where both a component and  its environment (other components) can be designed, by automata we find the theory of interface automata \cite {deAlfaro:2001} and conditional
